---
title: "linear model from Web"
author: "Claudia Cortez"
date: "Summer 2024"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Introduction 


Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

### Methods   
 All variables are numerical so we used the num num for all three parts.


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS  
### descriptive results  
### scatterplot  

```{r}
plot(SIMS~ARM,data=data)
```

This graph shows that the stronger your arms strength is the higher SIMS gets. 

### scatterplot

### Numerical results
```{r}
cor(SIMS~ARM,data=data)
```
  The correlation shows that the since 0.6860 is a positive. This means that the higher your strength the higher the SIMs because if the correlation was a negative it would decrease. 

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```


#### scatterplot with model fit
  
```{r}
plot(SIMS~ARM,data=data)
abline(model.1, col= 'red')
```
 
 The p-values for the intercept and slope is 0.000000000000000022.

#### Predict at target point


```{r}
newdata = data.frame(ARM = 88, GRIP=94)
predict(model.1, newdata, interval='pred')
```
 The SIMS predictions arm =88 is 0.7, the perdition interval is(-1.73,3.14.)

## Model 2 SIM~GRIP
### Decriptive Results - scatterplot 
```{r}
plot(SIMS~GRIP,data=data)
```
 
 This shows that the more grip you have the higher the simulation will also increase.    


### Now add in scatterplot


### Numerical results 
```{r}
cor(SIMS~GRIP,data=data)
```
 This shows that since your grip the strong the simulation will be positive outcome. 


### Inferential  (Build model.2)

```{r}
model.2 <-lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

#### scatterplot with model fit
  
```{r}
plot(SIMS~GRIP,data=data)
abline(model.2, col= 'red')
```

 The p-values for the intercept and slope is 0.000000000000000022 . 


#### predict model.2 at target point
```{r}
newdata = data.frame(ARM = 88, GRIP=94)
predict(model.2, newdata, interval='pred')
```
 The SIMs prodection for GRIP-94 is -0.5 and the prediction interval is (-3.10,2.03).


## Model 3 SIM~ARM+GRIP
 predication interval of SIMS given a value of 94for GRIP and 88 for ARM 

#### Numerical Results 
```{r}
df = data.frame(SIMS=data$SIMS, GRIP=data$GRIP, ARM=data$ARM)
cov (df)
```
 The correlation matrix shows that SIMS coorelates with GRIP and ARM:and GRIP correlates with SIMS. 


### Numerical results (cor)
```{r}
cor(SIMS~ARM+GRIP,data=data)
```

 This the correlation between the SIMS score and the two variables ARMS and GRIP. 

### Inferential  (Build 2-dimentional model.3)
```{r}
model.3 <-lm(SIMS~ ARM +GRIP, data=data)
summary.lm(model.3)
```

 The p-value from the F-statistic is 0.0000000000000002 This means the data fits the model, intercept p-value is 0.0000000000000002 ARM p-value 0.000000001 and the GRIP p-value is 0.000004. They are lower than 0.05.
P-value 0.0000000000000002 from the model parpmetes : intercepts, coefficient of ARM and coefficient of grip. 


#### predict model.3 at target point
 prediction interval of SIMS given a value of 94 for GRIP and 
88 for ARM . 

```{r}
newdata = data.frame(GRIP=94, ARM=88)
predSIMS = predict (model.3, newdata, interval = 'pred')
print(predSIMS)
```
 
 The predicted SIMS score for GRIP=94, ARM=88 is 0.150. The interval perdications are -2.13, 2.43.
 
### Moddel.1 model.3
```{r}
model.1=lm(SIMS~ ARM, data =data)
anova(model.1,model.3)
summary.lm(model.1)
```
 This anova shows that there is a difference in the models p-value is 0.000004, Model 2: SIMS`~ ARM + GRIP is better than model 1 SIMS~ ARM because the rss is 218 and in model 2 was 188. 
 
### Model.2 vs Model.3
```{r}
model.2=lm(SIMS~ GRIP, data=data)
anova(model.2, model.3)
summary.lm(model.1)
```
 Model SIMS~ ARM +GRIP is better than model SIMs~ GRIP because the rss is lower( 188)the p-value 0.0000000014

### Informally compare model 1 with model 2 

```{r}
summary.lm(model.1)
summary.lm(model.2)
```
 Model 1 SIMS ~ ARM is better than model 2 SIMs ~ GRIP because the rss for model 1 was lower than modele 2. 


