---
title: "linear model from Web"
author: "Claudia Cortez"
date: "Summer2024"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Introduction 


Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 # Methods
 All 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS  
### descriptive results  
### scatterplot  

```{r}
plot(SIMS~ARM,data=data)
```
This graph shows that the stonger your arms strength is the higher SIMS gets. 

### scatterplot

### Numerical results
```{r}
cor(SIMS~ARM,data=data)
```
The correlation shows that the since 0.6860 is a positive. This means that the higher your strength the higher the SIMs because if the coorelation was a negative it would decrese. 

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

```{r}
plot(SIMS~ARM,data=data)
abline(model.1, col= 'red')
```
The p-values for the intercept and slope is 0.000000000000000022 we reject the null. 

#### Predict at target point


```{r}
newdata = data.frame(ARM = 88, GRIP=94)
predict(model.1, newdata, interval='pred')
```
The SIMS predictions arm =88 is 0.7, the perdition interval is() -1.73,3.14.


#### scatterplot with model fit
  

## Model 2 SIM~GRIP

### Now add in scatterplot


### Numerical results 


### Inferential  (Build model.2)
  

#### predict model.2 at target point

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

`
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

